\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

Let us highlight some innovations in the contributions presented in this paper. First, the generic heterosynaptic model is formalized from first principles for optimal detection of the event-based spatiotemporal motifs, whereas [] uses a correlation-based heuristic, which we have proven to be less efficient. Moreover, in comparison to HOTS~\citep{lagorce_hots_2017} the weights are explainable as they directly inform on the logit (inverse sigmoid of the probability) of detecting each spatio-temporal spiking pattern. Another novelty is that the model simultaneously learns the weights and the delays, while for example the polychronization model~\citep{Izhikevich 2006} only learns the weights using STDP while the delays are randomly drawn and their values frozen. Moreover, the model is evaluated on a realistic task, while models such as tempotron are tested on simplified problems~\citep{gutig_tempotron_2006}. The main contribution is to provide a model that is suitable for any type of spatio-temporal spiking patterns and that can be trained in a supervised way by providing a dataset of supervision pairs. This allows for a more flexible definition of the model using this properly labeled dataset instead of relying on a careful description of the physical rules governing a task, e.g., the luminance conservation principle for motion detection~\citep{benosman_asynchronous_2012, dardelet}.

>>>>

Let us highlight some innovations in the contributions presented in this paper. First, the generic heterosynaptic model is formalized from first principles for optimal detection of the event-based spatiotemporal motifs, whereas [] uses a correlation-based heuristic, which we have proven to be less efficient. Moreover, in comparison to HOTS~\citep{lagorce_hots_2017} the weights are explainable as they directly inform on the logit (inverse sigmoid of the probability) of detecting each spatio-temporal spiking pattern. Another novelty is that the model simultaneously learns the weights and the delays, while for example the polychronization model~\citep{Izhikevich 2006} only learns the weights using STDP while the delays are randomly drawn and their values frozen. Moreover, the model is evaluated on a realistic task, while models such as tempotron are tested on simplified problems~\citep{gutig_tempotron_2006}. The main contribution is to provide a model that is suitable for any type of spatio-temporal spiking patterns and that can be trained in a supervised way by providing a dataset of supervision pairs. This allows for a more flexible definition of the model using this properly labeled dataset instead of relying on a careful description of the physical rules governing a task, e.g., the luminance conservation principle for motion detection~\citep{benosman_asynchronous_2012, dardelet_event-by-event_2021}.
